Interest Flooding Attack and Countermeasures in Named Data Networking

### 2013-01-15 08-conclusion.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@934 df1a90cd-247b-4364-bdaf-287a704eb499
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@937 df1a90cd-247b-4364-bdaf-287a704eb499

\section{Conclusion{\color{red}-needs a pass}}
\label{sec:conclusion}

@@

NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks. As a first step in this unexplored space, in this paper we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users. We then leverage the key features of the NDN architecture to design, develop and evaluate three mitigation strategies.
We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers so that they cause little or no service impact on legitimate users.

NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}. Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation.

>>>>

\section{Conclusion}
\label{sec:conclusion}

@@

NDN is a newly proposed future Internet architecture, thus it is important to address its resilience in face of DDoS attacks. As a first step in understanding the DDoS threats in NDN, we first examined a specific instance of DDoS attacks, Interest flooding, and the severe service degradation such an attack may cause to legitimate users. We then leverage the key features of the NDN architecture to design, develop and evaluate three mitigation strategies.
We performed detailed simulations on a range of topologies to quantify the effectiveness of our algorithms.   
The most effective algorithm---satisfaction-based pushback---was successful in almost completely shutting down the attackers so that they cause little or no service impact on legitimate users.

NDN's stateful forwarding plane enables a number of desired functions, such as loop-free, multipath data delivery, built-in multicast, scalable content delivery, effective flow balancing (i.e., congestion avoidance), and robust recovery from network failures, that people have attempted to install in IP networks~\cite{adaptive-forwarding}. Although this useful per-packet state can be abused to launch attacks, the demonstrated success of satisfaction-based pushback algorithm serves as an evidence that one can indeed utilize the per packet state built into each NDN router to enable effective DDoS mitigation as well.

%<<<<<<< .mine
%NDN is a new networking paradigm that shifts the emphasis from endpoints to addressing content directly, thereby enabling secure and efficient content distribution. However, the resilience of this new architecture to DoS and DDoS attacks has been relatively poorly understood. As a first step in understanding the DDoS threats in NDN, we describe one instance of DDoS attacks called Interest flooding and demonstrate the severe service degradation such an attack can cause to legitimate users. By leveraging and exploiting key features of the NDN architecture design, we also develop and evaluate three mitigation techniques, and perform detailed simulations on a range of topologies to quantify their effectiveness in mitigating interest flooding in NDN . 
%Our first strategy---Token bucket with per interface fairness---while easy to implement and deploy was ineffective at ensuring an acceptable %quality of service for legitimate users.  
%Our most effective algorithm---satisfaction-based pushback---was successful in almost completely eliminating the adverse effects of the attack over the network and resulted in minimal to no service impact for legitimate users. 
%Beyond our success with mitigating the particular attack in NDN, we strongly believe that the lessons from our experience with these mitigation algorithms as well as the metrics that we used to evaluate the effectiveness of our strategies can be applied to develop mitigation strategies for other classes of DDoS attacks in NDN as well.
%=======
%>>>>>>> .r936
